\Title

### 2020-03-04 manuscript/manuscript.tex
Rename interval for increment

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c | l l c c}
        \multicolumn{1}{c}{\textbf{Source layout}}
            & \multicolumn{1}{c}{\textbf{Depth type}}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \multicolumn{1}{c}{\textbf{Values}}
            & \multicolumn{1}{c}{\textbf{Interval}} \\
        \hline

        \multirow{5}{*}{Source Bellow Data}
            & Constant Depth
                & Depth (km)
                & \GroundSourceBellowDataConstantDepthDepth
                & \GroundSourceBellowDataConstantDepthDepthInterval \\
            \cline{2-5}
            & Relative Depth
                & Depth (km)
                & \GroundSourceBellowDataRelativeDepthDepth
                & \GroundSourceBellowDataRelativeDepthDepthInterval \\
            \cline{2-5}
            & \multirow{3}{*}{Variable Depth}
                & Depth (km)
                & \GroundSourceBellowDataVariableDepthDepth
                & \GroundSourceBellowDataVariableDepthDepthInterval \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                & \GroundSourceBellowDataVariableDepthDepthFactorInterval \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                & \GroundSourceBellowDataVariableDepthKNearestInterval \\
        \hline

        \multirow{8}{*}{Block median sources}
            & \multirow{2}{*}{Constant Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesConstantDepthDepth
                & \GroundBlockMedianSourcesConstantDepthDepthInterval \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundBlockMedianSourcesConstantDepthSpacingInterval \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                & \GroundBlockMedianSourcesRelativeDepthDepthInterval \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \GroundBlockMedianSourcesRelativeDepthSpacingInterval \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesVariableDepthDepth
                & \GroundBlockMedianSourcesVariableDepthDepthInterval \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                & \GroundBlockMedianSourcesVariableDepthDepthFactorInterval \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                & \GroundBlockMedianSourcesVariableDepthKNearestInterval \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \GroundBlockMedianSourcesVariableDepthSpacingInterval \\
        \hline

        \multirow{3}{*}{Grid Sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (km)
                    & \GroundGridSourcesConstantDepthDepth
                    & \GroundGridSourcesConstantDepthDepthInterval \\
            &
                & Spacing (km)
                    & \GroundGridSourcesConstantDepthSpacing
                    & \GroundGridSourcesConstantDepthSpacingInterval \\
            &
                & Pad
                    & \GroundGridSourcesConstantDepthPad
                    & \GroundGridSourcesConstantDepthPadInterval \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \AirborneSourceBellowDataConstantDepthDepth
                   & \AirborneBlockMedianSourcesConstantDepthDepth
                   & \AirborneGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesConstantDepthSpacing
                     & \AirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \AirborneGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBellowDataRelativeDepthDepth
                   & \AirborneBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesRelativeDepthSpacing
                     & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBellowDataVariableDepthDepth
                   & \AirborneBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
                  & \AirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}

>>>>

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c | l l c c}
        \multicolumn{1}{c}{\textbf{Source layout}}
            & \multicolumn{1}{c}{\textbf{Depth type}}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \multicolumn{1}{c}{\textbf{Values}}
            & \multicolumn{1}{c}{\textbf{Increment}} \\
        \hline

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (km)
                & \GroundSourceBellowDataConstantDepthDepth
                & \GroundSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataConstantDepthDamping
                & \GroundSourceBellowDataConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (km)
                & \GroundSourceBellowDataRelativeDepthDepth
                & \GroundSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataRelativeDepthDamping
                & \GroundSourceBellowDataRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (km)
                & \GroundSourceBellowDataVariableDepthDepth
                & \GroundSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                & \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                & \GroundSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataVariableDepthDamping
                & \GroundSourceBellowDataVariableDepthDampingIncrement \\
        \hline

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesConstantDepthDepth
                & \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesConstantDepthDamping
                & \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                & \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesRelativeDepthDamping
                & \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesVariableDepthDepth
                & \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                & \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                & \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesVariableDepthDamping
                & \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
        \hline

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (km)
                    & \GroundGridSourcesConstantDepthDepth
                    & \GroundGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (km)
                    & \GroundGridSourcesConstantDepthSpacing
                    & \GroundGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \GroundGridSourcesConstantDepthPad
                    & \GroundGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \GroundGridSourcesConstantDepthDamping
                    & \GroundGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c | l l c c}
        \multicolumn{1}{c}{\textbf{Source layout}}
            & \multicolumn{1}{c}{\textbf{Depth type}}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \multicolumn{1}{c}{\textbf{Values}}
            & \multicolumn{1}{c}{\textbf{Increment}} \\
        \hline

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (km)
                & \AirborneSourceBellowDataConstantDepthDepth
                & \AirborneSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataConstantDepthDamping
                & \AirborneSourceBellowDataConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (km)
                & \AirborneSourceBellowDataRelativeDepthDepth
                & \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataRelativeDepthDamping
                & \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (km)
                & \AirborneSourceBellowDataVariableDepthDepth
                & \AirborneSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBellowDataVariableDepthDepthFactor
                & \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBellowDataVariableDepthKNearest
                & \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataVariableDepthDamping
                & \AirborneSourceBellowDataVariableDepthDampingIncrement \\
        \hline

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (km)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                & \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (km)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                & \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                & \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (km)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                & \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (km)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                & \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                & \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (km)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                & \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                & \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (km)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                & \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                & \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
        \hline

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (km)
                    & \AirborneGridSourcesConstantDepthDepth
                    & \AirborneGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (km)
                    & \AirborneGridSourcesConstantDepthSpacing
                    & \AirborneGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \AirborneGridSourcesConstantDepthPad
                    & \AirborneGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \AirborneGridSourcesConstantDepthDamping
                    & \AirborneGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}
